---
title: "IMGD Climate Plots"
author: '@laneharrison'
date: "May 26, 2016"
output: rmarkdown::github_document
---

I re-plotted some of the IMGD Climate Survey.

The goal is to show the raw data in addition to the aggregate.

Each dot is a student's response.

Some questions led to varied responses-- these may be something we should at more closely.


```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)

master <- read.csv('data/data.csv')
source("fun.R")

key <- master[c(0, 1), ]
data <- master[-c(1, 2), ]
```

# Dividing by Majors

```{include=FALSE}
Majors | Minors | GraduateStudents | NonMajors
------ | ------ | ---------------- | ---------
67     | 13     | 11               | 53


LGBTQ | Male | Only White/Caucasian | Only Black/African American | Hispanic | Only American Indian/Alaskan Native | Only Other Race | More than One Race | First Generation College Students
- | - | - | - | - | - | - | - | - |
24.44 | 75.82 | 72.53 | 2.2 | 5.49 | 0.00 | 16.48 | 0.00 | 0.00 | 3.30 | 5.49
7.55 | 58.49 | 64.15 | 1.89 | 11.32 | 0.00 | 18.87 | 0.00 | 1.89 | 1.89 | 16.98

```
 
```{r}
unique(data$Source)

data$IMGDStatus <- ifelse(data$Q9_1==1, "Major",
                   ifelse(data$Q9_2==1, "Major",
                   ifelse(data$Q9_3==1, "Minor",
                   ifelse(data$Q9_4==1, "NonMajor",
                   ifelse(data$Q9_5==1, "NonMajor",
                   ifelse(data$Q8==5, "Graduate",
                          NA ))))))

# table(data$IMGDStatus)

```

# Dividing by Demographics

Majors, Minors, Graduate Students (n = 91)
Non-Majors (n = 53)

# Comparison Groupings

Privileged Male: White, Straight, Male AND IMGD Major, Minor, or Graduate Student

Answer | Frequency | Percent | Cumulative Percent
- | - | - | -
No | 45 | 49.45 | 49.45
Yes | 46 | 50.55 | 100
- | - | - | -
Total | 91 | 100 | 100

```{r}

data$Privileged <- 
    ifelse( 
      (data$IMGDStatus=="Major" | data$IMGDStatus=="Minor" | data$IMGDStatus=="Graduate") & 
      (data$Q4_1==1 & data$Q5==2 & data$Q1_1==1), "Privileged", 
    ifelse(
      (data$IMGDStatus=="Major" | data$IMGDStatus=="Minor" | data$IMGDStatus=="Graduate"), "NonPrivileged", 
    NA))

table(data$Privileged)

```

# Perceptions of Faculty

(`Q12_1` -- `Q12_11`)

```{r}

index <- c(
 "Q12_1",
 "Q12_2",
 "Q12_3",
 "Q12_4",
 "Q12_5",
 "Q12_6",
 "Q12_7",
 "Q12_8",
 "Q12_9",
 "Q12_10",
 "Q12_11"
)

xform <- function(d, V) {
d <- d[grep("^\\d+$", d[,V]),,drop=F]
d[,V] <- as.numeric(as.character(d[,V]))
return(d)
}

bplot <- function(V) {
  
caption <- key[1, V] 
caption <- paste0(strwrap(caption, 80), sep="", collapse="\n")
  
  p <- ggplot(data, aes_string("Privileged", V))
  p <- p + geom_boxplot(na.rm=TRUE) 
#  p <- p + geom_jitter(na.rm=TRUE)
  p <- p + geom_jitter(width=0.5, height=0.5, na.rm=TRUE)
  p <- p + expand_limits(y = c(1,4))
  p <- p + labs(caption=caption,x=element_blank())
  p <- p + coord_flip()
  p <- p + theme_bw()
  p <- p + theme(panel.border=element_blank())
  p <- p + theme(panel.grid.minor=element_blank())
  p <- p + theme(axis.ticks=element_blank())
  p <- p + theme(plot.caption=element_text(size=12, hjust=0, margin=margin(t=15)))
  p <- p + theme(text=element_text(family="PT Sans"))
  p
}

for (V in index){
  data <- xform(data, V)
  print( bplot(V) )
}

```

# Index 2: Feel Safe In Class

(`Q14_1` -- `Q14_4`)

```{r}

index <- c(
 "Q14_1",
 "Q14_2",
 "Q14_3",
 "Q14_4"
)

for (V in index){
  data <- xform(data, V)
  print( bplot(V) )
}

```

# Index 3: Diverse Materials

(`Q15_1` -- `Q15_3`)

```{r}

index <- c(
 "Q15_1",
 "Q15_2",
 "Q15_3"
)

for (V in index){
  data <- xform(data, V)
  print( bplot(V) )
}

```

# Index 4: Inclusive of Difference

```{r}

index <- c(
 "Q16_1",
 "Q16_2",
 "Q16_8",
 "Q16_9",
 "Q16_10"
)

for (V in index){
  data <- xform(data, V)
  print( bplot(V) )
}

```

# Index 5: Passionate Community

```{r}

index <- c(
 "Q16_2",
 "Q16_3",
 "Q16_4",
 "Q16_5",
 "Q16_6",
 "Q16_7"
)

for (V in index){
  data <- xform(data, V)
  print( bplot(V) )
}

```

# Index 6: Safety

```{r}

index <- c(
 "Q17_1",
 "Q17_2",
 "Q17_3",
 "Q17_4",
 "Q18_1",
 "Q18_2",
 "Q18_3",
 "Q19_1",
 "Q19_2",
 "Q19_3"
)

for (V in index){
  data <- xform(data, V)
  print( bplot(V) )
}

```

